Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-03-02 manuscript/manuscript.Rmd
Moved weighting function plot to plots.R

# Non-standard evaluation
d <- distribution <- method <- mean_lambda <- sd_lambda <- weight <- NULL

data_step <- data.table::data.table(x = seq(from=-1.0, to=1.0, by=0.001))
data_step[, "weight":=power.transform:::..weight_function_external(x, "step", k1=0.60)]

p_step <- ggplot2::ggplot(
  data = data_step,
  mapping = ggplot2::aes(
    x = x,
    y = weight))
p_step <- p_step + plot_theme
p_step <- p_step + ggplot2::geom_line()
p_step <- p_step + ggplot2::ggtitle(label="step")
p_step <- p_step + ggplot2::theme(
  plot.title=ggplot2::element_text(
    hjust=0.5,
    size=ggplot2::rel(1.0)))

data_triangle <- data.table::data.table(x = seq(from=-1.0, to=1.0, by=0.001))
data_triangle[, "weight":=power.transform:::..weight_function_external(x, "triangle", k1=0.30, k2=0.90)]

p_triangle <- ggplot2::ggplot(
  data = data_triangle,
  mapping = ggplot2::aes(
    x = x,
    y = weight))
p_triangle <- p_triangle + plot_theme
p_triangle <- p_triangle + ggplot2::geom_line()
p_triangle <- p_triangle + ggplot2::ggtitle(label="triangle")
p_triangle <- p_triangle + ggplot2::theme(
  plot.title=ggplot2::element_text(
    hjust=0.5,
    size=ggplot2::rel(1.0)),
  axis.text.y = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank())

data_cosine <- data.table::data.table(x = seq(from=-1.0, to=1.0, by=0.001))
data_cosine[, "weight":=power.transform:::..weight_function_external(x, "cosine", k1=0.30, k2=0.90)]

p_cosine <- ggplot2::ggplot(
  data = data_cosine,
  mapping = ggplot2::aes(
    x = x,
    y = weight))
p_cosine <- p_cosine + plot_theme
p_cosine <- p_cosine + ggplot2::geom_line()
p_cosine <- p_cosine + ggplot2::ggtitle(label="tapered cosine")
p_cosine <- p_cosine + ggplot2::theme(
  plot.title = ggplot2::element_text(
    hjust = 0.5,
    size = ggplot2::rel(1.0)),
  axis.text.y = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank())

p <- egg::ggarrange(plots=list(p_step, p_triangle, p_cosine), ncol=3, draw=FALSE)
p
```

>>>>

.plot_weighting_functions(plot_theme = plot_theme)
```
